Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
Midification de typos qui etaient encore là

    The rest of the paper is organized as follows: Section~\ref{sec:rel_works} reviews the related works relevant to our research. In Section~\ref{sec:data}, we detail the databases used in our analysis. Section~\ref{sec:overview} offers a reminder on existing methods. Section~\ref{sec:contrib} outlines our contributions. In Section~\ref{sec:res}, we present the results, analyzing the performance and implications of our proposed methods. Finally, Section~\ref{sec:ccl} concludes the paper and suggests directions for future research.

@@

\section{Contributions\label{sec:contrib}}
    \noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in section~\ref{sec:reminder}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all \acrshort{bs}s, without taking in account the difference of density.

>>>>

    The rest of the paper is organized as follows: Section~\ref{sec:rel_works} reviews the related works relevant to our research. In Section~\ref{sec:data}, we detail the databases used in our analysis. Section~\ref{sec:overview} offers an overview existing methods. Section~\ref{sec:contrib} outlines our contributions. In Section~\ref{sec:res}, we present the results, analyzing the performance and implications of our proposed methods. Finally, Section~\ref{sec:ccl} concludes the paper and suggests directions for future research.

@@

\section{Contributions\label{sec:contrib}}
    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of \acrshort{bs}s by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in section~\ref{sec:overview}, after having found potential neighbours for each \acrshort{bs}, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all \acrshort{bs}s, without taking in account the difference of density.
